Timeliness of security updates for Android

### 2014-08-05 securityupdates.tex
Add some user agent data graphs

\subsection{User-Agent data}
TODO

@@

>>>>

\subsection{User-Agent data}
Device Analyzer provides one view on the state of Android phones, however some of the data available in Device Analyzer can also be obtained from alternative sources.
OS version information for both Android and iOS (for which it is not possible to write a Device Analyzer app) is published in the User-Agent header sent by mobile devices making http requests.
We obtained data from the Apache web server access logs of the Student-Run Computing Facility\footnote{\url{https://www.srcf.net}} which hosts thousands of websites.
These data are shown in Figures \ref{fig:ua_android_month} and \ref{fig:ua_ios_month}.
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/ua-versions-android-month-norm}
 \caption{Versions of Android over time from SRCF User-Agent data}
 \label{fig:ua_android_month}
\end{figure}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{figures/ua-versions-ios-month-norm}
 \caption{Versions of iOS over time from SRCF User-Agent data}
 \label{fig:ua_ios_month}
\end{figure}
Clearly this data is nosier than the Device Analyzer data...
TODO

@@

\subsection{Predicting future version distributions}
TODO

\subsection{Lifetime of a vulnerability}
TODO
